Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2019-10-29 write-up/fda-recurrent.tex
Update fda-recurrent.tex
Updating the tex file to get the math right.

Given the basis for~$\beta(t)$, the model depends on choice of both~$K_b$ and~$K_x$.  We follow~\cite{Ruppert2002} by choosing $K_b$ large enough to prevent under-smoothing and~$K_x \geq K_b$ to satisfy identifiability constraints. While our theoretical analysis considers truncation levels that depend on~$n$, in practice, we follow the simple rule of thumb and set~$K_b = K_x = 35$. As long as the choices of~$K_x$ and $K_b$ are large enough, their impact on estimation is typically negligible. Below, we will exploit a connection between~\eqref{eq:approxscore} and score equations for a logistic regression model.  Before moving on, we introduce some additional notation.  First, let the baseline hazard $h_0(t; \gamma) := \exp(Z_{i,t}^\top \gamma)$ where~$Z_{i,t} \in \mathbb{R}^{q}$ parametrizes some piecewise-constant baseline   be :
\begin{equation}
\label{eq:approx_hazard}
h_i \left( t \given  H_{i,t}^{NX} ; \theta \right) \approx
\exp \left( Z_{i,t}^\top \gamma + g_t \left( H_{i,t}^{N} \right)^{\prime} \alpha
  + M_{i,t}^\top {\bf b} + C_{i,t}^\top J_{\hat \psi, \phi} {\bf b} \right)
= \exp \left( W_{i,t}^\top \theta \right),
\end{equation}
where~$\theta = (\gamma, \alpha, {\bf b})$ and~$\exp ( Z_{i,t}^\top \gamma) =: h_0 (t)$ is the parameterized baseline intensity function. We write~$\tilde U_n (\theta)$ to denote the approximate score function when substituting in~\eqref{eq:approx_hazard} for~\eqref{eq:hazardlinear}.

@@

\begin{lemma} \normalfont
\label{lemma:logistic}
Under weights~\eqref{eq:waage_weights} and the log-linear intensity
function~\eqref{eq:approx_hazard}, the approximate score
function~$\tilde U_n (\theta)$ is equivalent to
\[
\sum_{i=1}^n \sum_{t \in \bfT_i \cup D_i } \left[ {\bf 1}[t \in D_i]
  - \frac{1}{1 + \exp \left[- \left( \tilde{W}_{i,t}^\top \theta +
        \log \pi_i (t) \right) \right]} \right] \tilde{W}_{i,t}
\]
where~$\tilde W_{i,t} = -W_{i,t}$. This is the score function for
logistic regression with binary response~$Y_i(t)$ for $t \in N_i \cup
D_i$ and~$i \in [n]$ where~$Y_i(t) = 1[t \in N_i]$, offset~$\log \pi_i
(t)$, and covariates~$\tilde W_{i,t}$.
\end{lemma}

@@

Our theoretical analysis requires the several
assumptions, some regarding the subsampling procedure, some for the
event process, and some for the functional data. We state these
assumptions and then our main theorems.
We start by assuming there exists a~$\tau < \infty$ such that all
individuals are no longer at risk (i.e.,~$\tau_i < \tau$ for all~$i$).
Moreover, define $R_i (t)$ to be the at risk indicator for
participant~$i$.  That is,
\[
R_i (t) = \left \{ \begin{array}{c c} 1 & t \in (0,\tau_i) \\ 0
                                        & t > \tau_i\end{array} \right .
\]
Lemma~\ref{lemma:simpleasym} will be proven under regularity
conditions A-E in~\cite[pp. 420--421]{Andersen1993} along with the
following additional assumptions:

@@

We also require several assumptions due to the truncation of the
Karhunen-Lo{\`e}ve decomposition that represents~$X(t,s)$.
\begin{assumption}[Functional assumptions~\citep{Park2018}] \normalfont
\label{assumption:truncation}
The following assumptions are standard in prior work on longitudinal
functional data analysis~\citep{Park2018, Yao2005, ChenMuller2012}:
\begin{enumerate}[label=(A.\arabic*)]
\item\label{A1} $X = \{ X(s, T) : (s,T) \in \mathcal{S} \times
  \mathcal{T} \}$ is a square integrable element of the $L^2 (
  \mathcal{S} \times \mathcal{T})$
\item\label{A2} The sampling density~$g(T)$ is continuous
  and~$\sup |g(T)| < \infty$
\item\label{A3} $\E[X(s,T) X(s^\prime, T) X(s,T^\prime)
  X(s^\prime, T^\prime) ] < \infty$ for
  each $s,s^\prime \in [0,\Delta]$ and~$0 < T, T^\prime < \tau$.
\item\label{A4} $\E[\|X(\cdot, T)\|^4] < \infty$ for each~$0< T
  < \tau$.
\end{enumerate}
\end{assumption}
Assumption~\ref{A3} is guaranteed for by~\ref{E1} and~\ref{E3}, but is
stated here to emphasize its importance for the marginal covariance
procedure of~\cite{Park2018}.
Finally, for simplicity, we assume that there exists~$b^\star$
such that~$\beta(t) = \mathbold{\phi} (t) b^\star$; that is, the
true function~$\beta(t)$ sits in the span of the spline basis
expansion.
With the necessary assumptions stated, we can now state
Lemma~\ref{lemma:simpleasym}, which provides asymptotic theory.
\begin{lemma} \normalfont
\label{lemma:simpleasym}
Under Assumption~\ref{assumption:events},
Assumption~\ref{assumption:truncation}, and~$\Delta$ known, for
large~$n$ the estimator~$\hat \theta_n$ is consistent; moreover,
\[
\sqrt{n} (\hat \theta - \theta) \to N(0, \Xi (\theta)^{-1})
\]
where
\[
  \Xi (\theta) = \int_{0}^{\tau} w(s; \theta) \left[ \frac{h^{(1)}(s;
      \theta) \times  h^{(1)} (s;\theta)^{\top}}{h(s; \theta)} \right]
  ds.
\]
and~$\tau$ is the random censoring time of the event process.
\end{lemma}
An estimator for~$\Xi(\theta)$ is
\begin{equation}
\label{eq:fisher}
  \hat \Xi (\theta) = n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup D_i}
  w_i(t;\theta) (1-w_i(t;\theta)) \left[ \frac{h_i^{(1)}(t;
      \theta)}{h_i (t; \theta)} \right] \times  \left [
    \frac{h_i^{(1)} (t;\theta)}{h_i(t; \theta)} \right]^\top
\end{equation}
For the log-linear intensity model, the sampling-unbiased estimator
for~$\hat \Xi(\theta)$ is equivalent to the Fisher information for the
previously described logistic regression model.
This implies that subsampling from an inhomogeneous Poisson process,
standard logistic regression software can be used to fit the recurrent
event model by specifying an offset equal to~$\log \pi_i (t)$.
Not only this, Lemma~\ref{prop:optimal} shows
weights~\eqref{eq:waage_weights} are optimal within a particular class
of weighted estimating equations.

@@

\section{Simulation study}

@@

\section{A worked example: Adolescent psychiatric inpatient mHealth study}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:logistic}]
Recall~$\frac{d}{d\theta} \log h_i (t; \theta) = \frac{h^{(1)}_i (t;
  \theta)}{h_i (t; \theta)}$. Under the log-linear
intensity function given by~\eqref{eq:approx_hazard},
$\frac{d}{d\theta} \log h_i (t; \theta) = W_{i,t}$ and
\[
\frac{d}{d \theta} \log \left( \pi_i (t) + h_i (t;\theta) \right) =
\frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp
  \left( W_{i,t}^\top \theta \right)} W_{i,t}
\]
Therefore,
\begin{align*}
\tilde U_n (\theta)
  &= \sum_{i=1}^n \left \{ \sum_{t \in N_i} W_{i,t} -
    \sum_{t \in N_i \cup D_i} \frac{\exp \left( W_{i,t}^\top \theta
    \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)}
    W_{i,t} \right \} \\
  &= \sum_{i=1}^n \left \{ \sum_{t \in N_i} \frac{\pi_i (t)}{\pi_i (t)
    + \exp \left( W_{i,t}^\top \theta \right)} W_{i,t} -
    \sum_{t \in D_i} \frac{\exp \left( W_{i,t}^\top \theta
    \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)}
    W_{i,t} \right \} \\
  &= \sum_{i=1}^n \left \{ \sum_{t \in N_i} w_{i} (t; \theta) W_{i,t} -
    \sum_{t \in D_i} (1 - w_i (t; \theta)) W_{i,t} \right \} \\
  &= - \sum_{i=1}^n \sum_{t \in N_i \cup D_i} \left[ {\bf 1} [t \in
    D_i]  - w_{i} (t; \theta) \right] W_{i,t} \\
  &= \sum_{i=1}^n \sum_{t \in N_i \cup D_i}
    \left[ {\bf 1} [t \in D_i]  - \frac{1}{1 + \exp\left( - (
          \tilde W_{i,t}^\top \theta + \log (\pi_i (t) ) ) \right)}
    \right] \tilde W_{i,t}.
\end{align*}
where~$\tilde W_{i,t} = - W_{i,t}$. This is exactly the score equation
for logistic regression with offset~$\log \pi_i (t)$.
\end{proof}

@@

Asymptotic consistency is guaranteed~\cite[Theorem VI.1.1]{Andersen1993} if
\begin{equation}
\label{eq:andersen1}
n^{-1} \tilde U_n (\theta_0 ) \overset{P}{\to} 0,
\end{equation}
and
\begin{equation}
\label{eq:andersen2}
n^{-1} \frac{d}{d \theta^{\top}} \tilde U_n (\theta) \big |_{\theta =
  \theta_0} = \Xi (\theta),
\end{equation}
and
\begin{equation}
\label{eq:andersen3}
\lim_{n \to \infty} P \left( \left | n^{-1} \frac{d^2}{d \theta_j d
      \theta_k} \tilde U_n (\theta) \right | < M \text{ for all }
  j,k \text{ and all } \theta \in \Theta_0 \right) = 1
\end{equation}
To prove~\eqref{eq:andersen1}, we decompose~$\hat U_n (\theta_0)$ into
three terms
\[
n^{-1} \tilde U_n (\theta_0) = n^{-1} U_n (\theta_0 )  + n^{-1} \left(
  \hat U_n (\theta_0) - U_n (\theta) \right) + n^{-1} \left(\tilde U_n
  (\theta_0) - \hat U_n (\theta_0) \right)
\]
where, recall,~$\hat U_n (\theta_0)$ are the logistic score equations
with $\int_0^\infty X_i(t-s) \beta(s) ds$ and~$\tilde U_n (\theta_0)$
with the approximation~$C_{i,t}^\top J_{\phi, \psi} {\bf b}$.
\cite{Andersen1993} (Theorem VI.1.1) show that~$n^{-1} U_n (\theta_0)
\to 0$. The second term
\begin{align*}
n^{-1} \left( \hat U_n (\theta_0) - U_n (\theta_0) \right) =
  \frac{1}{n} \sum_{i=1}^n \int_0^{\tau} \frac{h^{(1)} (s;
  \theta_0)}{\pi_i (s) + h (s;\theta_0)} d M_i (s).
\end{align*}
where~$h(\cdot; \theta_0)$ is given by~\eqref{eq:hazardlinear}.
Lenglart's inequality \walt{check} implies the second term converges
in probability to zero under Assumptions~\ref{A1} and~\ref{A2}.

The third term satisfies
\begin{align*}
  &n^{-1} \left \| \hat U_n (\theta_0) - \tilde U_n (\theta_0) \right \| \\
  \leq & M n^{-1} \sum_{i=1}^n \sum_{t \in N_i \cup D_i} \bigg \| g
         \left( W_{i,t}^\top \theta  + \sum_{k=K_x+1}^\infty \hat
         c_{i,k} (t) \int_{t-\Delta}^t \hat \psi_k (s) \phi (s)^\top b
         + \log (\pi_i (t) ) \right) - g \left( \tilde W_{i,t}^\top
         \theta + \log (\pi_i (t)) \right) \bigg \| \\
&\leq M n^{-1} \sum_{i=1}^n \sum_{t \in N_i \cup D_i}
    \sup_{x \in \mathbb{R}} \left \| g^\prime \left( x \right)
  \right\| \times \left \| \sum_{k=K_x+1}^\infty \hat c_{i,k} (t)
  \sum_{l=1}^{K_b} \int_{t-\Delta}^t \hat \psi_k (s) \phi_l (s) b_l
  \right \| \\
&= \frac{M}{4} n^{-1} \sum_{i=1}^n \sum_{t \in N_i \cup D_i}
  \times \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(s,t) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| \\
&\to \frac{M}{4} \int_0^\tau \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(s,t) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| g(T) dT
\end{align*}
where~$M = \sup \| \tilde W_{i,t} \|$,~$g(x) = 1/(1+\exp(-x))$ is the
expit function.
The second inequality is due to the Taylor remainder theorem.
The third is due to~$g^\prime (x) = e^x/(1+e^x)^2 \leq e^0/(1+e^0)^2 =
1/4$, reordering the summation, and rewriting the error term in terms
of the difference between~$X(s,t)$ and the approximation with
truncation level~$K_x$. Letting~$n \to \infty$ allows us to re-write
the outside sums in terms of the integrated difference where the
integral is with respect to the sampling distribution~$g(T)$. Finally,
under Assumptions~\ref{assumption:truncation}, \cite{Park2018} show
\[
X(s,t) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \overset{p}{\to} 0
\]
as~$K_x \to \infty$, which implies the third term goes to zero as the
truncation level goes to infinity.
\end{proof}

>>>>

Given the basis for~$\beta(t)$, the model depends on choice of both~$K_b$ and~$K_x$.  We follow~\cite{Ruppert2002} by choosing $K_b$ large enough to prevent under-smoothing and~$K_x \geq K_b$ to satisfy identifiability constraints. While our theoretical analysis considers truncation levels that depend on~$n$, in practice, we follow the simple rule of thumb and set~$K_b = K_x = 35$. As long as the choices of~$K_x$ and $K_b$ are large enough, their impact on estimation is typically negligible. Below, we will exploit a connection between~\eqref{eq:approxscore} and score equations for a logistic regression model.  Before moving on, we introduce some additional notation. Define
\begin{equation}
\label{eq:approx_hazard}
h_i \left( t \given  H_{i,t}^{NX} ; \theta \right) \approx
\exp \left( Z_{t}^\top \gamma + g_t \left( H_{i,t}^{N} \right)^{\prime} \alpha
  + M_{i,t}^\top {\bf b} + C_{i,t}^\top J_{\hat \psi, \phi} {\bf b} \right)
= \exp \left( W_{i,t}^\top \theta \right),
\end{equation}
where~$\theta = (\gamma, \alpha, {\bf b})$ and~$\exp ( Z_{t}^\top \gamma) =: h_0 (t)$ is the parameterized baseline intensity function. We write~$\tilde U_n (\theta)$ to denote the approximate score function when substituting in~\eqref{eq:approx_hazard} for~\eqref{eq:hazardlinear}.

@@

\begin{lemma} \normalfont
\label{lemma:logistic}
Under weights~\eqref{eq:waage_weights} and the log-linear intensity function~\eqref{eq:approx_hazard}, the approximate score function~$\tilde U_n (\theta)$ is equivalent to
\[
\sum_{i=1}^n \sum_{t \in \bfT_i \cup D_i } \left[ {\bf 1}[t \in D_i]
  - \frac{1}{1 + \exp \left[- \left( \tilde{W}_{i,t}^\top \theta +
        \log \pi_i (t) \right) \right]} \right] \tilde{W}_{i,t}
\]
where~$\tilde W_{i,t} = -W_{i,t}$. This is the score function for logistic regression with binary response~$Y_i(t)$ for $t \in \bfT_i \cup \bfD_i$ and~$i \in [n]$ where~$Y_i(t) = 1[t \in \bfT_i]$, offset~$\log \pi_i (t)$, and covariates~$\tilde W_{i,t}$.
\end{lemma}

The connection to logistic regression allows our methodology to leverage ``off-the-shelf'' software.  The main complication is pre-processing of the functional data; however, these additional steps can also be taken care of via existing software.  Therefore, the entire data analytic pipeline is easy-to-implement and require minimal additional effort by the end-user. Before demonstrating the methodology via simulation in Section~\ref{section:simstudy}) and a worked example in Section~\ref{section:example}, we detail a theoretical analysis of our proposal.

@@

Our theoretical analysis requires assumptions regarding the subsampling procedure, the event process, and the functional data. We state these assumptions and then our main theorems. We start by assuming there exists a~$\tau < \infty$ such that all individuals are no longer at risk (i.e.,~$\tau_i < \tau$ for all~$i$). Moreover, define $R_i (t)$ to be the at risk indicator for participant~$i$, i.e., $R_i (t) = {\bf 1} [t \in (0,\tau_i)]$. Asymptotic theory provided in Lemma~\ref{lemma:simpleasym} will be proven under regularity conditions A-E in~\cite[pp. 420--421]{Andersen1993} along with the following additional assumptions:

@@

We also require several assumptions due to the truncation of the Karhunen-Lo{\`e}ve decomposition that represents~$X(t,s)$.
\begin{assumption}[Functional assumptions~\citep{Park2018}] \normalfont
\label{assumption:truncation}
The following assumptions are standard in prior work on longitudinal functional data analysis~\citep{Park2018, Yao2005, ChenMuller2012}:
\begin{enumerate}[label=(A.\arabic*)]
\item\label{A1} $X = \{ X(s, T) : (s,T) \in \mathcal{S} \times
  \mathcal{T} \}$ is a square integrable element of the $L^2 (
  \mathcal{S} \times \mathcal{T})$
\item\label{A2} The subsampling and conditional intensity rate functions~$g_y(T)$ are continuous
  and~$\sup |g_y(T)| < \infty$.
\item\label{A3} $\E[X(s,T) X(s^\prime, T) X(s,T^\prime)
  X(s^\prime, T^\prime) ] < \infty$ for
  each $s,s^\prime \in [0,\Delta]$ and~$0 < T, T^\prime < \tau$.
\item\label{A4} $\E[\|X(\cdot, T)\|^4] < \infty$ for each~$0< T
  < \tau$.
\end{enumerate}
\end{assumption}
Assumption~\ref{A3} is guaranteed by~\ref{E1} and~\ref{E3}, but is stated here to emphasize its importance for the marginal covariance procedure of~\cite{Park2018}. Finally, for simplicity, we assume that there exists~$b^\star$ such that~$\beta(t) = \mathbold{\phi} (t) b^\star$; that is, the
true function~$\beta(t)$ sits in the span of the spline basis expansion. With the necessary assumptions stated, we can now state Lemma~\ref{lemma:simpleasym}, which provides asymptotic theory.
\begin{lemma} \normalfont
\label{lemma:simpleasym}
Under Assumption~\ref{assumption:events},
Assumption~\ref{assumption:truncation}, and~$\Delta$ known, for
large~$n$ the estimator~$\hat \theta_n$ is consistent; moreover,
\[
\sqrt{n} (\hat \theta - \theta) \to N(0, \Xi (\theta)^{-1})
\]
where
\[
  \Xi (\theta) = \int_{0}^{\tau} w(s; \theta) \left[ \frac{h^{(1)}(s;
      \theta) \times  h^{(1)} (s;\theta)^{\top}}{h(s; \theta)} \right]
  ds.
\]
and~$\tau$ is the random censoring time of the event process.
\end{lemma}
An estimator for~$\Xi(\theta)$ is
\begin{equation}
\label{eq:fisher}
  \hat \Xi (\theta) = n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup D_i}
  w_i(t;\theta) (1-w_i(t;\theta)) \left[ \frac{h_i^{(1)}(t;
      \theta)}{h_i (t; \theta)} \right] \times  \left [
    \frac{h_i^{(1)} (t;\theta)}{h_i(t; \theta)} \right]^\top
\end{equation}
For the log-linear intensity model, the sampling-unbiased estimator
for~$\hat \Xi(\theta)$ is equivalent to the Fisher information for the
previously described logistic regression model.
This implies that subsampling from an inhomogeneous Poisson process,
standard logistic regression software can be used to fit the recurrent
event model by specifying an offset equal to~$\log \pi_i (t)$.
Not only this, Lemma~\ref{prop:optimal} shows
weights~\eqref{eq:waage_weights} are optimal within a particular class
of weighted estimating equations.

@@

\section{Simulation study} \label{section:simstudy}

@@

\section{A worked example: Adolescent psychiatric inpatient mHealth study} \label{section:example}

@@

\begin{proof}[Proof of Lemma~\ref{lemma:logistic}]
Recall~$\frac{d}{d\theta} \log h_i (t; \theta) = \frac{h^{(1)}_i (t; \theta)}{h_i (t; \theta)}$. Under the log-linear intensity function given by~\eqref{eq:approx_hazard}, $\frac{d}{d\theta} \log h_i (t; \theta) = W_{i,t}$ and
\[
\frac{d}{d \theta} \log \left( \pi_i (t) + h_i (t;\theta) \right) =
\frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp
  \left( W_{i,t}^\top \theta \right)} W_{i,t}
\]
Therefore,
\begin{align*}
\tilde U_n (\theta)
  &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} W_{i,t} - \sum_{t \in \bfT_i \cup \bfD_i} \frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)}  W_{i,t} \right \} \\
  &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} \frac{\pi_i (t)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)} W_{i,t} - \sum_{t \in \bfD_i} \frac{\exp \left( W_{i,t}^\top \theta \right)}{\pi_i (t) + \exp \left( W_{i,t}^\top \theta \right)} W_{i,t} \right \} \\
  &= \sum_{i=1}^n \left \{ \sum_{t \in \bfT_i} w_{i} (t; \theta) W_{i,t} -
    \sum_{t \in D_i} (1 - w_i (t; \theta)) W_{i,t} \right \} \\
  &= - \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \left[ {\bf 1} [t \in \bfD_i]  - w_{i} (t; \theta) \right] W_{i,t} \\
  &= \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
    \left[ {\bf 1} [t \in \bfD_i]  - \frac{1}{1 + \exp\left( - (
          \tilde W_{i,t}^\top \theta + \log (\pi_i (t) ) ) \right)}
    \right] \tilde W_{i,t}.
\end{align*}
where~$\tilde W_{i,t} = - W_{i,t}$. This is exactly the score equation
for logistic regression with offset~$\log \pi_i (t)$.
\end{proof}

@@

Asymptotic consistency is guaranteed~\cite[Theorem VI.1.1]{Andersen1993} if
\begin{equation}
\label{eq:andersen1}
n^{-1} \tilde U_n (\theta_0 ) \overset{P}{\to} 0,
\end{equation}
and
\begin{equation}
\label{eq:andersen2}
n^{-1} \frac{d}{d \theta^{\top}} \tilde U_n (\theta) \big |_{\theta =
  \theta_0} = \Xi (\theta),
\end{equation}
and
\begin{equation}
\label{eq:andersen3}
\lim_{n \to \infty} P \left( \left | n^{-1} \frac{d^2}{d \theta_j d
      \theta_k} \tilde U_n (\theta) \right | < M \text{ for all }
  j,k \text{ and all } \theta \in \Theta_0 \right) = 1
\end{equation}
To prove~\eqref{eq:andersen1}, we decompose~$\hat U_n (\theta_0)$ into
three terms
\[
n^{-1} \tilde U_n (\theta_0) = n^{-1} U_n (\theta_0 )  + n^{-1} \left(
  \hat U_n (\theta_0) - U_n (\theta) \right) + n^{-1} \left(\tilde U_n
  (\theta_0) - \hat U_n (\theta_0) \right)
\]
where, recall,~$\hat U_n (\theta_0)$ are the logistic score equations with $\int_0^\infty X_i(t-s) \beta(s) ds$ and~$\tilde U_n (\theta_0)$ with the approximation~$C_{i,t}^\top J_{\phi, \psi} {\bf b}$. \cite{Andersen1993} (Theorem VI.1.1) show that~$n^{-1} U_n (\theta_0)
\to 0$. The second term
\begin{align*}
n^{-1} \left( \hat U_n (\theta_0) - U_n (\theta_0) \right) =
  \frac{1}{n} \sum_{i=1}^n \int_0^{\tau} \frac{h^{(1)} (s;
  \theta_0)}{\pi_i (s) + h (s;\theta_0)} d M_i (s).
\end{align*}
where~$h(\cdot; \theta_0)$ is given by~\eqref{eq:hazardlinear}. Lenglart's inequality implies the second term converges in probability to zero under Assumptions~\ref{E1} and~\ref{E2}.

The third term satisfies
\begin{align*}
  &n^{-1} \left \| \hat U_n (\theta_0) - \tilde U_n (\theta_0) \right \| \\
  \leq & M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i} \bigg \| g
         \left( W_{i,t}^\top \theta  + \sum_{k=K_x+1}^\infty \hat
         c_{i,k} (t) \int_{t-\Delta}^t \hat \psi_k (s) \phi (s)^\top b
         + \log (\pi_i (t) ) \right) - g \left( \tilde W_{i,t}^\top
         \theta + \log (\pi_i (t)) \right) \bigg \| \\
&\leq M n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
    \sup_{x \in \mathbb{R}} \left \| g^\prime \left( x \right)
  \right\| \times \left \| \sum_{k=K_x+1}^\infty \hat c_{i,k} (t)
  \sum_{l=1}^{K_b} \int_{t-\Delta}^t \hat \psi_k (s) \phi_l (s) b_l
  \right \| \\
&= \frac{M}{4} n^{-1} \sum_{i=1}^n \sum_{t \in \bfT_i \cup \bfD_i}
  \times \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(s,t) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| \\
&\to \frac{M}{4} \int_0^\tau \sum_{l=1}^{K_b} \left \| \int_{t-\Delta}^t
  \left( X(s,t) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \right)
  \phi_l (s) b_l\right \| (g_0(T) + g_1(T)) dT
\end{align*}
where~$M = \sup \| \tilde W_{i,t} \|$,~$g(x) = 1/(1+\exp(-x))$ is the
expit function.
The second inequality is due to the Taylor remainder theorem.
The third is due to~$g^\prime (x) = e^x/(1+e^x)^2 \leq e^0/(1+e^0)^2 =
1/4$, reordering the summation, and rewriting the error term in terms
of the difference between~$X(s,t)$ and the approximation with
truncation level~$K_x$. Letting~$n \to \infty$ allows us to re-write
the outside sums in terms of the integrated difference where the
integral is with respect to the sampling distribution~$g(T)$. Finally,
under Assumptions~\ref{assumption:truncation}, \cite{Park2018} show
\[
X(s,t) - \sum_{k=1}^{K_x} \hat c_{i,k} (t) \psi_k (s) \overset{p}{\to} 0
\]
as~$K_x \to \infty$, which implies the third term goes to zero as the
truncation level goes to infinity.

The same argument can be used in conjunction under assumptions~\ref{E1} and~\ref{E4} to prove~\eqref{eq:andersen2}.
\end{proof}
